---
title: "Week 4 Part 1 - Confidence Intervals and Ttests"
author: "Michelle Shteyn"
date: "10/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Confidence intervals

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)

```
The mean length of sea otters calculated is 42.22 with a standard deviation of .., and the 95% confidence interval is 34.69 to 49.75 inches. The 95% confidence interval means that, if we took 100 samples of otters, in 95 of the confidence intervals we could expect to find the true population mean.

## T-tests (1-sample t-test)

See a claim: mean otter length is 50 inches. 

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test

```
There's a 4.44% chance that I could have randomly picked a sample from my population mean that is at least as different from 50 as this 42.22 value.


## Two-sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28,31,40,42,26,29,31)

t.test(x = desert_bighorns, y = sierra_bighorns)
```

-9.653212 11.046069 this is the expected confidence interval for the difference in mean sizes in horn length. The CI on the difference in means is not usually reported.
This p value tells me that if these samples are drawn from population with the same mean horn length (null) then there is almost a 90% that I could have retrieved my samples from populations with the same mean and gotten means for my samples that are at least as different as mine are. 

it is the probability, if samples were drawn from pops with the same mean value, that we could've gotten samples with means that are at least as different as ours are. If that prob is really high, then it's really likely that we drew these samples from a pop with the same mean. 
















